My title

### 2022-03-22 outputs/paper/paper.Rmd
Remove huakun.R which is a draft script. Write comments for all other scripts I wrote.

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Lantao Cui
  - Huakun Shen
  - Sijian Wu
thanks: "Code and data are available at: https://github.com/HuakunShen/Discrimination-Analysis-Canadian-2014-GSS"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "We studied discrimination in Canada and its related effect. Discrimination could potentially to inequality and even crimes. We found that sex discrimination is most common, the most common place for discrimination to happen is bank, store and retaurant; there is no apparent gender discrimination in law enforcement; and robbery is correlated with discrimination."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Lantao Cui
  - Huakun Shen
  - Sijian Wu
thanks: "Code and data are available at: https://github.com/HuakunShen/Discrimination-Analysis-Canadian-2014-GSS"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "We studied discrimination in Canada and its related effects. Discrimination could potentially to inequality and even crimes. We found that sex discrimination is most common, the most common place for discrimination to happen is bank, store and retaurant; there is no apparent gender discrimination in law enforcement; and robbery is correlated with discrimination."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

## Limitations
